### 2020-08-10 data/draft-sections.tex
hyperlinks with title

>>>>

\subsection{List of Visitors to the Department}
\item Dr.~Malabika Pramanik, University of British Columbia, Vancouver, Canada, August 2, 2017--August 2, 2017.
\item Dr.~Jugal Verma, IIT Bombay, September 5, 2017--September 5, 2017.
\item Dr.~Anirban Basak, Weizmann Institute, Rehovot, Israel, October 5, 2017--October 8, 2017.
\item Dr.~Neeraj Kayal, Microsoft Research, Bangalore, October 6, 2017--October 6, 2017.
\item Dr.~Nishant Chandgotia, Tel Aviv University, Israel, October 7, 2017--October 10, 2017.
\item Dr.~Krishanu Roy, IMSc, Chennai, November 20, 2017--November 24, 2017.
\item Dr.~Patrice Philippon, CNRS, Paris, France, November 22, 2017--November 22, 2017.
\item Dr.~Kyoung-Seog Lee, Center for Geometry and Physics, Institute for Basic Science (IBS) Pohang, Republic of Korea, December 4, 2017--December 4, 2017.
\item Dr.~Ved Datar, University of California, Berkeley, USA, January 3, 2018--January 3, 2018.
\item Dr.~Moumanti Podder, Georgia Institute of Technology, Atlanta, USA, January 7, 2018--January 12, 2018.
\item Dr.~Augusto Visintin, Universita' degli Studi di Trento, Italy, January 10, 2018--January 13, 2018.
\item Dr.~Alexander Bufetov, CNRS, Marseilles, France; and Steklov Mathematical Institute, Moscow, Russia, January 11, 2018--January 20, 2018.
\item Dr.~Shreedevi K. Masuti, IMSc, Chennai, January 11, 2018--January 11, 2018.
\item Dr.~Jayadev Athreya, University of Washington, Seattle, USA, January 17, 2018--January 17, 2018.
\item Dr.~Krishna B. Athreya, Iowa State University, Ames, USA, January 19, 2018--January 19, 2018.
\item Dr.~Pranav Pandit, IHES, Bures-sur-Yvette, France, January 31, 2018--January 31, 2018.
\item Dr.~Svante Linusson, KTH, Stockholm, Sweden, February 3, 2018--February 11, 2018.
\item Dr.~Samu Potka, KTH, Stockholm, Sweden, February 3, 2018--February 11, 2018.
\item Dr.~Dominique Guillot, University of Delaware, Newark, USA, February 4, 2018--February 16, 2018.
\item Dr.~Aprameyan Parthasarathy, Universität Paderborn, Germany, March 1, 2018--April 27, 2018.
\item Dr.~Mahesh Kakde, King's College, London, UK, March 2, 2018--March 2, 2018.
\item Dr.~Arnab Saha, Australian National University, Canberra, Australia, March 4, 2018--March 10, 2018.
\item Dr.~Koushik Ramachandran, Oklahoma State University, Stillwater, USA, March 6, 2018--March 7, 2018.
\item Dr.~Vikas Krishnamurthy, Schrodinger Institute, Vienna, Austria, March 6, 2018--March 6, 2018.
\item Dr.~Subhajit Goswami, IHES, Bures-sur-Yvette, France, March 19, 2018--March 19, 2018.
\item Dr.~Sarang Sane, IIT Madras, March 23, 2018--March 23, 2018.
\item Dr.~Siegfried Böcherer, Universität Mannheim, Germany, March 24, 2018--April 8, 2018.
\item Dr.~Ananthnarayan Hariharan, IIT Bombay, April 6, 2018--April 7, 2018.
\item Dr.~C. S. Aravinda, TIFR-CAM, Bangalore, April 6, 2018--April 6, 2018.
\item Dr.~Bidyut Sanki, IMSc, Chennai, April 24, 2018--April 29, 2018.
\item Dr.~Satyajit Guin, IISER Mohali, April 25, 2018--April 25, 2018.
\item Dr.~Prashant Jha, Louisiana State University, Baton Rouge, USA, May 1, 2018--May 1, 2018.
\item Dr.~Ramesh Kasilingam, ISI Bangalore, May 4, 2018--May 4, 2018.
\item Dr.~Radhika Ganapathy, TIFR, Mumbai, May 24, 2018--May 24, 2018.
\item Dr.~Luz Roncal, BCAM, Bilbao, Spain, June 1, 2018--August 31, 2018.
\item Dr.~Terrence George, Brown University, Providence, USA, June 2, 2018--June 30, 2018.
\item Dr.~Aprameyan Parthasarathy, Universität Paderborn, Germany, June 3, 2018--June 23, 2018.
\item Dr.~Sudhir Ghorpade, IIT Bombay, June 4, 2018--June 4, 2018.
\item Dr.~Yifei Chen, Chinese Academy of Sciences, Beijing, China, June 5, 2018--June 12, 2018.
\item Dr.~Rajeeva L. Karandikar, CMI, Chennai, June 27, 2018--June 28, 2018.
\item Dr.~Soumyashant Nayak, University of Pennsylvania, Philadelphia, USA, June 27, 2018--June 27, 2018.
\item Dr.~M. S. Raghunathan, CBS, Mumbai, June 28, 2018--June 29, 2018.
\item Dr.~Shubham Sinha, UCSD, San Diego, USA, July 1, 2018--July 30, 2018.
\item Dr.~Terrence George, Brown University, Providence, USA, July 2, 2018--August 8, 2018.
\item Dr.~Anand Deopurkar, Australian National University, Canberra, Australia, July 2, 2018--July 4, 2018.
\item Dr.~Asilata Bapat, Australian National University, Canberra, Australia, July 2, 2018--July 4, 2018.
\item Dr.~Mizanur Rahaman, University of Waterloo, Canada, July 9, 2018--July 11, 2018.
\item Dr.~Kunal Datta, INRIA, Sophia-Antipolis, France, July 23, 2018--July 25, 2018.
\item Dr.~Sumana Hatui, HRI, Allahabad, July 23, 2018--July 23, 2018.
\item Dr.~Neha Prabhu, Queen's University, Kingston, Canada, July 23, 2018--July 23, 2018.
\item Dr.~Bhimarthi Ravinder, CMI, Chennai, July 26, 2018--July 27, 2018.
\item Dr.~Tulasi Ram Reddy, NYU Abu Dhabi, UAE, July 31, 2018--August 12, 2018.
\item Dr.~Ravi Raghunathan, IIT Bombay, August 3, 2018--August 3, 2018.
\item Dr.~Jayadev Athreya, University of Washington, Seattle, USA, August 10, 2018--August 10, 2018.
\item Dr.~Stephan Baier, RKMVU, Belur, August 26, 2018--August 27, 2018.
\item Dr.~A. Raghuram, IISER Pune, September 24, 2018--September 26, 2018.
\item Dr.~Bharatram Rangarajan, Hebrew University, Jerusalem, Israel, September 26, 2018--September 26, 2018.
\item Dr.~Amritanshu Prasad, IMSc, Chennai, September 27, 2018--September 28, 2018.
\item Dr.~Jean Baptiste Gatsinzi, Botswana University of Science and Technology, Botswana, October 1, 2018--October 31, 2018.
\item Dr.~Dootika Vats, University of Warwick, UK, October 3, 2018--October 4, 2018.
\item Dr.~Ashutosh Kumar, NUS, Singapore, October 9, 2018--October 12, 2018.
\item Dr.~Dhruv Ranganathan, IAS Princeton, MIT Boston (USA); CMI (Chennai); Cambridge (UK), October 29, 2018--November 2, 2018.
\item Dr.~K. N. Raghavan, IMSc, Chennai, November 9, 2018--November 9, 2018.
\item Dr.~Daniel Seco, ICMAT, Madrid, Spain, November 13, 2018--November 14, 2018.
\item Dr.~Purvi Gupta, Rutgers University, New Brunswick, USA, November 18, 2018--November 23, 2018.
\item Dr.~Anuradha Sharma, IIIT Delhi, December 3, 2018--December 3, 2018.
\item Dr.~Harald Upmeier, Universität Marburg, Germany, December 4, 2018--February 28, 2019.
\item Dr.~Sameer Chavan, IIT Kanpur, December 10, 2018--December 13, 2018.
\item Dr.~Katharina Jochemko, KTH, Stockholm, Sweden, December 11, 2018--December 14, 2018.
\item Dr.~Alexander Belton, University of Lancaster, UK, December 12, 2018--December 21, 2018.
\item Dr.~Gopal Srinivasan, IIT Bombay, December 13, 2018--December 13, 2018.
\item Dr.~Thorsten Heidersdorf, Max Planck Institut, Bonn, Germany, December 18, 2018--December 20, 2018.
\item Dr.~Rongwei Yang, SUNY Albany, USA, December 19, 2018--December 21, 2018.
\item Dr.~Prasad Tetali, Georgia Institute of Technology, Atlanta, USA, January 1, 2019--January 1, 2019.
\item Dr.~T. V. H. Prathamesh, University of Innsbruck, Austria, January 3, 2019--January 4, 2019.
\item Dr.~Oscar Ciaurri, Universidad de la Rioja, Logronyo, Spain, January 7, 2019--January 25, 2019.
\item Dr.~Dominique Guillot, University of Delaware, Newark, USA, January 10, 2019--January 17, 2019.
\item Dr.~Ramesh Gangolli, University of Washington, Seattle, USA, January 13, 2019--January 26, 2019.
\item Dr.~Sanjay Ramassamy, École Normale Supériure, Paris, France, January 13, 2019--January 26, 2019.
\item Dr.~Hiroshige Shiga, Tokyo Institute of Technology, Japan, January 17, 2019--January 26, 2019.
\item Dr.~Pranav Pandit, ICTS Bangalore, January 21, 2019--January 21, 2019.
\item Dr.~Niranjan Balachandran, IIT Bombay, January 29, 2019--January 30, 2019.
\item Dr.~Siegfried Böcherer, Universität Mannheim, Germany, January 31, 2019--February 10, 2019.
\item Dr.~Mohan R., ISI Bangalore, February 8, 2019--February 8, 2019.
\item Dr.~Nishant Chandgotia, Hebrew University, Jerusalem, Israel, February 11, 2019--February 12, 2019.
\item Dr.~Arpan Kabiraj, CMI, Chennai, February 11, 2019--February 11, 2019.
\item Dr.~Nishad Kothari, University of Campinas, São Paulo, Brazil, February 13, 2019--February 13, 2019.
\item Dr.~James Cann, University College London, UK, February 15, 2019--March 10, 2019.
\item Dr.~Klas Pettersson, University of Tromsø – The Arctic University of Norway, February 26, 2019--February 26, 2019.
\item Dr.~Parthanil Roy, ISI Bangalore, March 1, 2019--March 1, 2019.
\item Dr.~Xavier Viennot, CNRS and LaBRI, France, March 6, 2019--March 9, 2019.
\item Dr.~Agnid Banerjee, TIFR-CAM, Bangalore, March 8, 2019--March 8, 2019.
\item Dr.~Ravi A. Rao, TIFR, Mumbai, March 9, 2019--March 15, 2019.
\item Dr.~Soma Maity, IISER Kolkata, March 10, 2019--March 12, 2019.
\item Dr.~Agnid Banerjee, TIFR-CAM, Bangalore, March 15, 2019--March 15, 2019.
\item Dr.~Soumya Bhattachrarya, IISER Kolkata, March 17, 2019--March 23, 2019.
\item Dr.~Sayan Chakraborty, ISI Kolkata, April 8, 2019--April 8, 2019.
\item Dr.~Jyotirmoy Ganguly, IISER Pune, April 14, 2019--April 19, 2019.
\item Dr.~Siegfried Böcherer, Universität Mannheim, Germany, April 22, 2019--April 22, 2019.
\item Dr.~Indrava Roy, IMSc, Chennai, April 28, 2019--April 30, 2019.
\item Dr.~Vineeth Chintala, IIT Bombay, May 1, 2019--May 1, 2019.
\item Dr.~Sankaran Viswanath, IMSc, Chennai, May 3, 2019--May 7, 2019.
\item Dr.~Amritanshu Prasad, IMSc, Chennai, May 8, 2019--May 8, 2019.
\item Dr.~Sudipto Choudhury, IIT Bombay, May 20, 2019--May 22, 2019.
\item Dr.~Siddhartha Sahi, Rutgers University, New Brunswick, USA, June 2, 2019--June 6, 2019.
\item Dr.~Sanjay P. K., NIT Calicut, June 5, 2019--June 30, 2019.
\item Dr.~Sanjay Parui, NISER, Bhubaneswar, June 9, 2019--June 24, 2019.
\item Dr.~Sasmita Patnaik, IIT Kanpur, June 23, 2019--June 28, 2019.
\item Dr.~Shubham Sinha, UCSD, San Diego, USA, June 24, 2019--July 2, 2019.
\item Dr.~Subhajit Goswami, IHES, Bures-sur-Yvette, France, July 24, 2019--July 27, 2019.
\item Dr.~Marc Hubert-Nicole, University of Marseilles, France, July 28, 2019--September 2, 2019.
\item Dr.~Rakesh, University of Delaware, Newark, USA, August 2, 2019--August 2, 2019.
\item Dr.~Terrence George, Brown University, Providence, USA, August 7, 2019--August 7, 2019.
\item Dr.~Akashdeep Dey, Princeton University, Princeton, USA, August 12, 2019--August 16, 2019.
\item Dr.~Hariharan Narayanan, TIFR, Mumbai, August 14, 2019--August 14, 2019.
\item Dr.~Piyush Srivastava, TIFR, Mumbai, August 14, 2019--August 14, 2019.
\item Dr.~Nikhil Srivastava, University of California, Berkeley, USA, August 16, 2019--August 16, 2019.
\item Dr.~Mahan Mj, TIFR, Mumbai, August 25, 2019--August 31, 2019.
\item Dr.~T. V. H. Prathamesh, KREA University, Sricity, August 28, 2019--August 30, 2019.
\item Dr.~Soumyashant Nayak, University of Pennsylvania, Philadelphia, USA, August 28, 2019--August 29, 2019.
\item Dr.~Soumik Pal, University of Washington, Seattle, USA, August 30, 2019--August 30, 2019.
\item Dr.~Chandan Dalawat, HRI, Allahabad, September 2, 2019--September 6, 2019.
\item Dr.~Guhan Venkat, Université Laval, Quebec, Canada; Morningside Center of Mathematics, Beijing, China, September 4, 2019--September 7, 2019.
\item Dr.~Senthil Raani, IISER Berhampur, September 6, 2019--September 11, 2019.
\item Dr.~Jean-Marie de Koninck, Université Laval, Quebec, Canada, September 11, 2019--September 13, 2019.
\item Dr.~Rekha Biswal, Max Planck Institut, Bonn, Germany, September 13, 2019--September 17, 2019.
\item Dr.~Prasad Tetali, Georgia Institute of Technology, Atlanta, USA, September 13, 2019--September 13, 2019.
\item Dr.~Kartick Adhikari, Technion, Haifa, Israel, September 15, 2019--September 20, 2019.
\item Dr.~Martin Kreuzer, Universität Passau, Germany, September 16, 2019--October 1, 2019.
\item Dr.~Anantha Padmanabha, IMSc, Chennai, September 18, 2019--September 20, 2019.
\item Dr.~Santosh Nadimpalli, Radboud University, Nijmegen, Netherlands, September 19, 2019--September 21, 2019.
\item Dr.~Divyang Bhimani, TIFR-CAM, Bangalore, September 20, 2019--September 20, 2019.
\item Dr.~Sushmita Venugopalan, IMSc, Chennai, September 21, 2019--September 29, 2019.
\item Dr.~Rajeeva L. Karandikar, CMI, Chennai, September 27, 2019--September 27, 2019.
\item Dr.~Gianluca Faraco, TIFR, Mumbai, October 7, 2019--October 10, 2019.
\item Dr.~Atul Dixit, IIT Gandhinagar, October 9, 2019--October 11, 2019.
\item Dr.~Aswin Balasubramanian, Rutgers University, New Brunswick, USA, October 14, 2019--October 14, 2019.
\item Dr.~Uri Onn, Australian National University, Canberra, Australia, October 23, 2019--October 30, 2019.
\item Dr.~Souvik Pal, HRI, Allahabad, October 24, 2019--November 2, 2019.
\item Dr.~Sorin Dumitrescu, Université Côte d'Azur, Nice, October 26, 2019--October 30, 2019.
\item Dr.~Indranil Biswas, TIFR Mumbai, October 26, 2019--October 30, 2019.
\item Dr.~Ramesh Manna, TIFR-CAM, Bangalore, October 30, 2019--October 30, 2019.
\item Dr.~Tathagata Basak, Iowa State University, Ames, USA, November 4, 2019--November 4, 2019.
\item Dr.~Apratim Chakraborty, ISI Bangalore, November 4, 2019--November 4, 2019.
\item Dr.~Chandrasheel Bhagwat, IISER Pune, November 6, 2019--November 6, 2019.
\item Dr.~Klas Pettersson, UiT – The Arctic University of Norway, Narvik, Norway, November 6, 2019--November 6, 2019.
\item Dr.~Harald Upmeier, Universität Marburg, Germany, November 7, 2019--March 15, 2020.
\item Dr.~Uri Onn, Australian National University, Canberra, Australia, November 8, 2019--November 9, 2019.
\item Dr.~Bernhard Heim, German University of Technology, Oman, November 14, 2019--November 14, 2019.
\item Dr.~Luz Roncal, BCAM, Bilbao, Spain, November 21, 2019--December 7, 2019.
\item Dr.~Sugata Mondal, TIFR, Mumbai, November 21, 2019--November 21, 2019.
\item Dr.~Pavol Hell, Simon Fraser University, Canada, November 22, 2019--November 22, 2019.
\item Dr.~Gianluca Faraco, TIFR, Mumbai, November 26, 2019--December 4, 2019.
\item Dr.~Indranath Sengupta, IIT Gandhinagar, November 27, 2019--November 29, 2019.
\item Dr.~Vyjayanthi Chari, University of California, Riverside, USA, December 1, 2019--December 31, 2019.
\item Dr.~John Meakin, University of Nebraska, Lincoln, USA, December 3, 2019--December 4, 2019.
\item Dr.~Anne Schilling, University of California, Davis, USA, December 14, 2019--December 16, 2019.
\item Dr.~Amritanshu Prasad, IMSc, Chennai, December 14, 2019--December 16, 2019.
\item Dr.~Sankaran Viswanath, IMSc, Chennai, December 14, 2019--December 16, 2019.
\item Dr.~K. N. Raghavan, IMSc, Chennai, December 14, 2019--December 16, 2019.
\item Dr.~Tanushree Khandai, IISER Mohali, December 14, 2019--December 16, 2019.
\item Dr.~Bhimarthi Ravinder, IIT Tirupati, December 14, 2019--December 16, 2019.
\item Dr.~Sachin Sharma, IIT Kanpur, December 14, 2019--December 16, 2019.
\item Dr.~Sunil Chhita, Durham University, December 16, 2019--December 19, 2019.
\item Dr.~Ken Ono, University of Virginia, Charlottesville, USA, December 18, 2019--December 18, 2019.
\item Dr.~Sujatha Ramdorai, University of British Columbia, Vancouver, Canada, December 20, 2019--December 20, 2019.
\item Dr.~Akshaa Vatwani, IIT, Gandhinagar, February 26, 2020--February 26, 2020.
\item Dr.~Arijit Chakrabarty, ISI, Kolkata, February 26, 2020--.
\item Dr.~Debapratim Banerjee, ISI, Kolkata, March 9, 2020--March 11, 2020.

### 2020-08-10 data/reports.tex
hyperlinks with title

In a joint work with Pritam Ganguly  we have investigated the $ L^p $  boundedness of the lacunary maximal function $ M_{\H^n}^\lac $ associated to the spherical means $ A_r f$  taken over Koranyi spheres on the Heisenberg group. Closely following an approach used by M. Lacey in the Euclidean case, we obtain sparse bounds for these maximal functions leading to new unweighted and weighted estimates. The key ingredients in the proof are the $L^p$  improving property of the operator $ A_r $  and a continuity property of the difference $ A_r f−\tau_y A_r f,$ where $\tau_yf(x)=f(xy−1) $ is the right translation operator.

>>>>

In a joint work with Pritam Ganguly  we have investigated the $ L^p $  boundedness of the lacunary maximal function $ M_{\mathbb{H}^n}^l $ associated to the spherical means $ A_r f$  taken over Koranyi spheres on the Heisenberg group. Closely following an approach used by M. Lacey in the Euclidean case, we obtain sparse bounds for these maximal functions leading to new unweighted and weighted estimates. The key ingredients in the proof are the $L^p$  improving property of the operator $ A_r $  and a continuity property of the difference $ A_r f−\tau_y A_r f,$ where $\tau_yf(x)=f(xy−1) $ is the right translation operator.
